\documentclass{article}
\usepackage{enumerate}

\begin{document}
\title{CSC361: Assignment 0}
\author{Paul MacKay}

\maketitle

\begin{itemize}
	\item \textit {things you already know about computer networks: } \newline
		Basic concepts like shortest path using graph abstraction, issues with networks in third world countries.
		Configuring networks on Linux machines, DNS filtering like quad9 and google dns. Internet privacy standards
		like the introduction of HTTPS, back-end website creation (using a bash script), certifying domain with crontab.
	\item \textit {things you want to know more about computer networks }\newline
		Computer networks is an integral part of computing I want to learn more about it so that I can apply that
		knowledge for personal projects and job opportunites.
	\item \textit {what and how's your home Internet access?} \newline
		I use wireless network at my house and get around 80 - 200 Mbit/s
	\item \textit {how can we help you and others better?} \newline
		Having a student forumn for questions would be helpful. Also video lectures would be useful for review.
		Posting textbook overviews (what will be on the midterm) for exam preparation.
	\item \textit {interested in ACM/IEEE, NSERC USRA, JCURA?} \newline
		Yes, I plan on applying for coop for the summer/fall term.
	\item \textit {any issues with logistics? volunteer for course rep?} \newline
		I'm not aware of any problems with logistics. N/A
	\item \textit {set your brightspace and teams profile picture accurately and consistently} \newline
		Ok.
	\item \textit {let me know you as well! for reference letters later etc} \newline
		Hi my name is Paul, I am interested in tinkering and learning as much as possible about computers,
		so that in the future I may work on/create a project(s) that will better the lives of people. I like using
		Linux, and Vim for development.
\end{itemize}

\end{document}
